Plots_GAM

### 2024-05-23 Output/PLOSRound2/ResponsetoReviewers.txt

Figure S4 — It is very hard to see the fit lines other than the pooled fit. Consider using different colors 
and solid lines since this is online.

Table 1: The trees described in the legend should be included in the supplemental material.

Fig 11: Despite the fact that it is explained in the legend, the figure should probably indicate that O2 
values are log Km, or else put actual values on the log-scale Y axis. Also, the axis should indicate the 
units for Km. Finally, why is the red band so narrow compared to the green and blue?

We apologize for the omissions. We have revised the axis labels to make the log scaling more noticeable. The narrowness of the red bar (spanning 230 to 280 µM) should also be more apparent with the new scaling.

@@

L757: The authors should specify that this is a DNA repair ligase, not the DNA ligase that seals Okazaki 
fragments during DNA replication (assuming this is the case).

Thank you for your comment, the revised text now reads "DNA repair ligase".  
Lines XXX:

### 2024-05-23 Code/Plots_GAM.Rmd
Fixed GAM plot for SS120

# Generate GAM for red light conditions for all strains using chlorophyll proxy logistic growth rate. 
```{r GAM separate niches hypervolume for red light}
GamWL = c("deltaOD") #deltaOD or OD720
GamParaMod = "Lmu" # logistic model growth estimates
GamVar = "660" # growth spectral wavelength
ErrorTolGrowth = 30 # the amplitude tolerance of the standard error of the fitted growth estimates
ErrorTol = 30 # the amplitude tolerance of the standard error of the fitted GAM

@@

# Generate GAM for blue light conditions for all strains using chlorophyll proxy logistic growth rate. 
```{r GAM separate niches hypervolume for blue light}
GamWL = c("deltaOD") #deltaOD or OD720
GamParaMod = "Lmu" # logistic model growth estimates
GamVar = "450" # growth spectral wavelength
ErrorTolGrowth = 30 # the amplitude tolerance of the standard error of the fitted growth estimates
ErrorTol = 30 # defined for the GAM fit

>>>>

# Generate GAM for red light conditions for all strains using chlorophyll proxy logistic growth rate. 
```{r GAM separate niches hypervolume for red light}
GamWL = c("deltaOD") #deltaOD or OD720
GamParaMod = "Lmu" # logistic model growth estimates
GamVar = "660" # growth spectral wavelength
ErrorTolGrowth = 30 # the amplitude tolerance of the standard error of the fitted growth estimates
ErrorTol = 35 # the amplitude tolerance of the standard error of the fitted GAM

@@

# Generate GAM for blue light conditions for all strains using chlorophyll proxy logistic growth rate. 
```{r GAM separate niches hypervolume for blue light}
GamWL = c("deltaOD") #deltaOD or OD720
GamParaMod = "Lmu" # logistic model growth estimates
GamVar = "450" # growth spectral wavelength
ErrorTolGrowth = 30 # the amplitude tolerance of the standard error of the fitted growth estimates
ErrorTol = 35 # defined for the GAM fit
